---
title: "R Consortium R Submission Pilot 5 - Summary Tables and Figures"
author: "Pilot 5 Team"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
- \usepackage{pdfpages}
---

Note : In Pilot 5, following the same approach as Pilot1, different open-source packages were used when generating each of the 4 analysis outputs to test wider use case scenarios. The outputs were formatted differently intentionally to cover different company specific formatting choices.

\newpage

```{r path, echo=FALSE}
library(stringr)

path <- list(
  sdtm = file.path("/cloud/project/pilot5-submission/pilot5-input/sdtmdata"),
  adam = file.path("/cloud/project/pilot5-submission/pilot5-input/adamdata"),
  output = file.path("/cloud/project/pilot5-submission/pilot5-output//pilot5-tlfs"),
  adam_json = file.path("/cloud/project/pilot5-submission/pilot5-output/pilot5-datasetjson")
)
```

#### Table 14-2.01

#### Summary of Demographic and Baseline Characteristics

```{r demog, echo=FALSE, message=FALSE, comment=NA, out.height="400px", out.width="40%"}
source("/cloud/project/pilot5-submission/pilot5-programs/tlf-demographic.r")
print(tbl)
```

\newpage

#### Table 14-3.01

#### Primary Endpoint Analysis: ADAS Cog (11) - Change from Baseline to Week 24 - LOCF

```{r adadas, echo=FALSE, message=FALSE, comment=NA, out.height="400px", out.width="40%"}
source("/cloud/project/pilot5-submission/pilot5-programs/tlf-primary.r")
print(tbl)
```

\newpage

#### Table 14-3.02

#### Primary Endpoint Analysis: Glucose (mmol/L) - Summary at Week 20 - LOCF

```{r glucose, echo=FALSE, message=FALSE, comment=NA, out.height="400px", out.width="40%"}
source("/cloud/project/pilot5-submission/pilot5-programs/tlf-efficacy.r")
print(tbl)
```

\newpage

#### Figure 14-1

#### Time to Dermatologic Event by Treatment Group

```{r plot, echo=FALSE}
# Ensure to print the plot object `km` correctly
source("/cloud/project/pilot5-submission/pilot5-programs/tlf-kmplot.r")
```

\includepdf[pages=-]{"/cloud/project/pilot5-submission/pilot5-output/pilot5-tlfs/pdf/tlf-kmplot-pilot5.pdf"}

