---
title: "R Consortium R Submission Pilot 5 - Summary Tables and Figures"
author: "Pilot5 Team"
date: "`r Sys.Date()`"
format:
  pdf:
    latex-engine: xelatex
    geometry: "margin=0.25in"
    header-includes:
      - \usepackage{pdfpages}
      - \usepackage{graphicx}
geometry: "margin=0.25in"
header-includes:
  - \usepackage{pdfpages}
  - \usepackage{graphicx}
---
  
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.height = 6)
```

Note : In Pilot 5, following the same approach as Pilot1, different open-source packages were used when generating each of the 4 analysis outputs to test wider use case scenarios. The outputs were formatted differently intentionally to cover different company specific formatting choices.

\newpage

#### Table 14-2.01
#### Summary of Demographic and Baseline Characteristics

```{r demog, echo=FALSE, message=FALSE, comment=NA}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%")

library(here)

source("pilot5-helper-fcns.r")
path <- list(
  sdtm = here("pilot5-submission", "pilot5-input", "sdtmdata", "datasetjson"),
  adam = here("pilot5-submission", "pilot5-input", "adamdata"),
  output = here("pilot5-submission", "pilot5-output", "pilot5-tlfs"),
  adam_json = here("pilot5-submission", "pilot5-output", "pilot5-datasetjson"),
  programs = here("pilot5-submission", "pilot5-programs")
)

source(file.path(path$programs, "tlf-demographic.r"))
print(tbl)
```

\noindent\begin{minipage}[t]{\textwidth}
  \begin{flushleft}
    {\large \textbf{Table 14-3.01}}\\[1ex] 
    {\large \textbf{Primary Endpoint Analysis: ADAS Cog (11) - Change from Baseline to Week 24 - LOCF}}
  \end{flushleft}
  \vspace{4ex}
  \begin{center}
    \includegraphics[scale=1]{cmb-report-manual-files/tlf-efficacy-pilot5.pdf}
  \end{center}
\end{minipage}





